\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-23 paper/experiments.tex
Update query in paper

\section{Experiments}\label{sec:experiments}
To evaluate the performance of our approach,  we implemented
a prototype system in Java, following a traditional iterator model.
For our experiments we plan and execute queries
for two separate survey-based data sets, showing that our system
is ideal for early dataset exploration.

>>>>

\section{Experiments}
To evaluate the performance of our approach,  we implemented
a prototype system in Java, following a traditional iterator model.
For our experiments we plan and execute queries
for two separate survey-based data sets, showing that our system
is ideal for early dataset exploration.
